\documentclass[hidelinks]{ctexart}

\usepackage[margintoc,singleton,epu]{van-de-la-sehen}
\usepackage{van-le-trompe-loeil}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{positioning}
\usetikzlibrary{matrix}
\usepackage{pxrubrica}
\usepackage{tipa}

\def\katanode#1#2#3#4#5#6{%
    \draw node[draw, regular polygon, regular polygon sides=4, minimum height=2cm, draw=cyan, line width=0.4mm, fill=cyan!15!white, #1, inner sep=-2mm](#2) {\Large #3};
    \draw (#2.corner 1) node[below left] {\small\textsf{\phantom{Hj}#4}};
    \draw (#2.corner 2) node[below right] {\footnotesize\color{lightgray}\textit{#5}};
    \draw (#2.side 3) node[above] {\footnotesize \color{lightgray} #6};
}

\def\hiranode#1#2#3#4#5#6{%
    \draw node[draw, regular polygon, regular polygon sides=4, minimum height=2cm, draw=yellow!80!black, line width=0.4mm, fill=yellow!45!white, #1, inner sep=-2mm](#2) {\Large #3};
    \draw (#2.corner 1) node[below left] {\small\textsf{\phantom{Hj}#4}};
    \draw (#2.corner 2) node[below right] {\footnotesize\color{lightgray}\textit{#5}};
    \draw (#2.side 3) node[above] {\footnotesize \color{lightgray} #6};
}

\newlist{citemize}{itemize}{3}
\setlist[citemize,1]{noitemsep,topsep=0pt,label={-},leftmargin=1em}

\begin{document}

\showtitle{Miscellaneous}

\newpoint{alleviate} to make (suffering, deficiency, or a problem) less severe.
\\
\href{https://www.google.com/amp/s/www.internationalscienceediting.com/how-to-use-respectively-correctly/amp/}{to use `respectively' correctly}\\
\href{https://www.nature.com/articles/nphys411}{Green function or Green's function}
\newpoint{split infinitive} a construction consisting of an infinitive with an adverb or other word inserted between to and the verb.
\newpoint{raison d'\^ etre} the most important reason or purpose for someone or something's existence.
\newpoint{panacea} a solution or remedy for all difficulties or diseases.
\newpoint{tallyho} a huntsman's cry to the hounds on sighting a fox; a simple greeting.
\newpoint{tallywhacker} penis.
\newpoint{ansatz} an educated guess or an additional assumption made to help solve a problem, and which is later verified to be part of the soluton by its results.
\newpoint{YMMV, Your mileage may vary} One person's experience with a product may be different from another's.
\newpoint{(with) tongue in cheek} without really meaning what one is saying or writing.
\newpoint{femboy} a cisgender young male as effeminate in disparaging or desirable way.
\newpoint{ground coffee} coffee beans are grinded and prepared to be brewed in a coffee machine or hand pour.
\\
The past tense and past participle of `grind' is `ground'.
\newpoint{eunuch} a man who has been castrated.
\\
Martini - Martinus\\
\newpoint{henceforth/henceforward/henceforwards} from now on.
\newpoint{here}
\begin{citemize}
    \item herein: within this content, context, or thing. e.g. that if he be not fully satisfied herein.
    \item hereinafter: in the parts of this document, statement, or book that follow.
    \item hereinbefore: in a preceding part of this speech, book, or text.
    \item heretofore: prior to now; until now.
    \item hereabout/hereabouts: close to; nearby.
    \item hereafter: in time to come; from now on.
    \item herebefore: before now.
    \item hereby: by this means, action, or process.
    \item hereof: of this; concerning this.
    \item hereon: on this place; to this place.
\end{citemize}
See \href{https://en.wiktionary.org/wiki/hereon}{here-, there- and where- words}.
\newpoint{whither} to what place; to where.
\newpoint{whence} from where; from which place.
\newpoint{hither} to this place; to here; over here.
\newpoint{hence} from here; from this place.
\newpoint{thither} to that place.
\newpoint{thence} from there; from that place or from that time.
\\
\href{https://english.stackexchange.com/questions/32217/what-is-meant-by-pun-intended}{pun intended}
\newpoint{hipocrisy} the pratice of claiming to have moral standards or belief to which one's own behaviour does not conform; pretense.
\newpoint{cross-check} verify by using an alternative source or method.
\\
\href{http://commonerrorscalendar.blogspot.com/2013/04/volumnvolume-common-errors-in-english.html?m=1#:~:text=The%20archaic%20spelling%20of%20%22volumn,the%20e%20and%20the%20n.}{on `volumn' and `volume'}.
\\
\href{https://english.stackexchange.com/questions/96162/is-it-correct-to-say-i-kindly-request-you-to}{Polite usage `we kindly'}.
\begin{citemize}
    \item We kindly request ...
    \item We politely request ...
    \item We humbly request ...
    \item We respectfully request ...
    \item We earnestly request ...
\end{citemize}
\href{https://english.stackexchange.com/questions/31980/why-themselves-and-himself}{Why `themselves' and `himself'}.

\end{document}
