\documentclass{ctexart}

\usepackage{van-de-la-sehen}

\title{The Universe History: from Big Bang and Inflation to Dark Epoch with Possible Future Singularity}
\date{}

\begin{document}

\maketitle
Main problem: physical law of universe changes. Thus to construct the universe history, it's like to reconstruct the complete mirror with a single broken piece. Some laws of nature are known, like gravity force by falling of objects. But we don't know why it goes in this way.
\par
\section{Introduction} % (fold)
\label{sec:introduction}

Fundamental interaction in the universe are
\begin{cenum}
    \item electromagnetic;
    \item weak;
    \item strong;
    \item gravitational: we see every day, but understand much less than other three. Other three are quantum by nature, and are described by waves. But for grativational wave, it's only guessed to be quantum.
\end{cenum}
Not clear if there are more or not. No exceptions have been seen, but it doesn't exclude their existence. These four are already complicated, as the universe is changing and thus the physical laws.
\par
Electroweak $SU_2$ theory proposed by Yang-Mills is one example of unification of interaction. Another is the Grand Unified Models (GUT, $SU_5$).
\par
Discovery of gravitational waves implies that Gravity is also Quantum Theory.
\par
Great puzzle: What is Quantum Gravity. Different approaches: perturbative QG, loop QG, String theory, M-theory, or something else, where String theory is one limit case of M-theory. 
\par
We are looking for a unified theory to describe the universy history. By definition, Einstein could not construct a unified theory, not only because strong interaction were not discovered then, but also because of the evolving theory then.

% section introduction (end)

\section{Univere History} % (fold)
\label{sec:univere_history}

The Big Bang is the point where the universy is with infinite energy and not spacetimes. We don't know Where/Why/How the unverse started, nor do we know the Fundamental Singularity. At the very beginning, the universe was a point.
\par
Question: How to describe the evolution of the universe. Describing the track of bike riding from school to home is done by locating the position, constructing coordinate on the map. The universe is described by $4$ coordintes $x,y,z,t$. It looks formally that these four are totally equivalent, including $t$ as equal-footing to the other three, but not fully understood, and we are not sure if and why $t$ is really special.
\par
First moment of universe creation: inflation --- the early time acceleration occurs. We introduce time-dependent radius of the universe (the scale factor), $a=a\pare{t}$. The analog of distance is 4-dimensional space is defined as
\[ \rd{s^2} = -\rd{t}^2 + a^2\pare{t}\pare{\rd{x^2} + \rd{y^2} + \rd{z}^2}. \]
The signature of the metric is Minkowski-like $\pare{-1,1,1,1}$ instead of Euclidean $\pare{1,1,1,1}$. If $a\pare{t}$ grows then the universe expands. If its second derivative is positive then universe expands with acceleration.
\begin{cenum}
    \item The early universe is eventually de Sitter spacetime when $a\pare{t} = \exp Ht$.
    \item Quick inflation occurred but exited. If quick expanding continued, then nothing could be created.
    \item Transition into Creation of radiation (radiation era) and matter (matter dominance era, when galaxies are created). So-Called Dark component of universe.
    \item After inflation, the universe expanded with deceleration.
\end{cenum}
What are the sources of inflation? Possible proposals includes quantum gravity, some fundamental fields, or some fundamental fluid or cosmological constant. Why it was stopped by exit from exponetial expansion?

\subsection{Dark Energy} % (fold)
\label{sub:dark_energy}

Some 6000000000 years ago decelerated expansion is substituted by accelerated expansion. At that Dark Energy era, the curvature of our universe is very small.
\begin{cenum}
    \item $p = k\rho$, where $p$ is the effective universe pressure, $k$ is a constant and $\rho$ is the effective universe energy-density.
    \item $\rho$ of Dark Energy is about $70\%$.
    \item $\rho$ of Dark Matter is about $25\%$.
    \item $\rho$ of usual matter is about $5\%$. This includes galaxies.
\end{cenum}
The Question of EoS (Equation of State) parameter $k$:
\begin{cenum}
    \item $k$ is about $-1$;
    \item if $k<-1$, we live is phantom DE universe, which is unstable;
    \item if $k=-1$, the universe is governed by cosmological constant, which is the effective vacuum, the quantum field there;
    \item if $-1 < k < -1/3$, we have quintessence;
    \item Observations indicate $k=-1$ with $3\%$ to $5\%$ accuracy;
    \item In case of phantom DE, $a\pare{t} = \displaystyle \rec{\pare{t-\const}^n}$. The pressure would soon diverge and enters singularity, going back to the Big Bang where no spacetime exists, disaster to any civilization.
\end{cenum}
For phantom and quintessence DE there may appera FUTURE singularity at about 30-50 billion years from now. The interesting question is which singularity may occur in the future.
\begin{cenum}
    \item Type I (Big rip): for $t = \const$, all $a\pare{t}$, energy-density and pressure diverge.
    \item Type II (Sudden): for $t = \const$ only pressure diverges, which may occur is some but not all quintessence universe.
    \item Type III: $a\pare{t}$ is regular but pressure and energy-density diverge at $t=\const$.
    \item Type IV: all quantities are regular but higher order geometric invariants may diverge.
    \item Other possibilities include regular eternal expansion, deceleration or so.
\end{cenum}
Very accurate observation should be done to make vigorous prediction to the future. Type may also varies by region, and the transition is not understood.

% subsection dark_energy (end)

% section univere_history (end)

\section{The Universe Evolution and Extended Gravity} % (fold)
\label{sec:the_universe_evolution_and_extended_gravity}

\subsection{De Sitter universe induced by quantum effects} % (fold)
\label{sub:de_sitter_universe_induced_by_quantum_effects}

Different models may be adopted.

% subsection de_sitter_universe_induced_by_quantum_effects (end)

\subsection{Motivations to Modify Gravity for Universe Description} % (fold)
\label{sub:motivations_to_modify_gravity_for_universe_description}

\begin{cenum}
    \item The necessity to account quantum effects at Plank level.
    \item Modified gravity provides the very natural gravity alternative for dark energy.
    \item Modified gravity presents very natural unification of the early times inflation and late-time acceleration.
    \item Assuming that universe is entering the phantom phase, modified gravity describes the transition from non-phantom phase to phantom one naturally.
\end{cenum}

% subsection motivations_to_modify_gravity_for_universe_description (end)

% section the_universe_evolution_and_extended_gravity (end)

\end{document}
